\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textbf{$|$ {#2}} & \textbf{\small #3} \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\myProjectSubheading}[5]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\textbf{#1} $|$ \emph{#2}} & \textbf{\small #3} \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\myProjectSubheadingNoSub}[5]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\textbf{#1} $|$ \emph{#2}} & \textbf{\small #3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\specialResumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \bfseries{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small{#1}} & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\header}[5]{
    \noindent
    {\LARGE\bfseries{#1} 
     \hfill 
     \small\raisebox{-0.1\height}\faPhone\ {#2} 
     \href{mailto:tkhall03@gmail.com}{\raisebox{-0.2\height}\faEnvelope\
     \underline{#3}} 
     \href{https://github.com/tkhall03}{\raisebox{-0.2\height}\faGithub\
     \underline{#4}} -
     \bfseries{#5}
     }
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\header{Thomas Hall}{207-381-7246}{tkhall03@gmail.com}{github.com/tkhall03}{College Station, TX}
        
\vspace{-8pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Texas A\&M University}{3.5/4.0}{May 2025}
      {Bachelor of Science in Computer Science, Minor in Cybersecurity and Mathematics}{College Station, TX}
      
  \resumeSubHeadingListEnd

\vspace{-15pt}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- Present}
      {Aramco - Houston Research Center}{Houston, TX}
      \resumeItemListStart
        \resumeItem{Co-developed the autonomous downhole robot KASHF “Kinetic Autonomous Sensing in High Fidelity” for use in oil wells which will lead to significant cost savings for the Company.}
        \resumeItem{Engineered software and communication protocols between robots and personally developed Android application.}
        \resumeItem{Worked on firmware for custom high temperature microcontrollers to be used in downhole robots.}
        \resumeItem{Worked with Bluetooth LE to develop a communication framework that could be implemented in multiple robots.}
      \resumeItemListEnd

    \resumeSubheading
      {Offshore Software Engineering Intern}{May 2022 -- August 2022}
      {TDI Brooks International}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Worked offshore in the Gulf of Mexico and Atlantic Ocean deploying experimental Viber-core technology for survey of wind farms and deep-sea oil rigs/pipelines.}
        \resumeItem{Worked on developing data analysis and visualization software for piston and box cores.}
        \resumeItem{Conducted tests as efficiently and precisely as possible to avoid sample backlog during unpredictable weather conditions.}
    \resumeItemListEnd

    \specialResumeSubheading
        {Geotechnical Laboratory Technician}{May 2021 -- August 2021}
        {TDI Brooks International}{May 2020 -- August 2020}
        \resumeItemListStart
        \resumeItem{Conducted geotechnical tests such as Atterberg Limits, Soil Composition, Grain size, and vane shear test. \hspace{1mm}}
        \resumeItem{Expedited critical testing results without compromising sample validity or quality assurance.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, C, Java, Python, HTML/CSS, JavaScript, MySQL} \\ 
     \textbf{Frameworks}{: ReactJS, Next.js, Tailwind CSS, Flask} \\
    }}
 \end{itemize}
 \vspace{-20pt}
 
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \myProjectSubheading{Code for Good Hackathon}{React, Next.js, Flask, Tailwind CSS}{October 2023}{JPMorgan Chase \& Co}{Plano, TX}
          \resumeItemListStart
            \resumeItem{Competed with a group of students to design and develop a full stack application for the non profit Mothers Against Drunk Driving.}
            \resumeItem{Developed a user interface using React that featured leaderboards, driving reports, and various utilities. This interface used a custom API built in Next.js to communicate with the backend.}
            \resumeItem{Implemented backend with Flask; when given user location data over the course of a drive, it generated a driving score using an algorithm design by our team.}
          \resumeItemListEnd
          \vspace{-7pt}
          
      \myProjectSubheading{Computer Vision Team Lead}{Python, OpenCV, YOLOv8}{September 2022 – August 2023}{TAMU Robomasters}{College Station, TX}
          \resumeItemListStart
            \resumeItem{As the elected head of the computer vision team lead the team to update the vision model from YOLOv5 to YOLOv8.}
            \resumeItem{Implemented new multiple armor plate detection using Roboflow and OpenCV. Developed Kalman filters to improve aiming and tracking precision.}
          \resumeItemListEnd 
          \vspace{-7pt}

        \myProjectSubheading{Expatriate Graveyard Database}{MySQL, C}{June 2018}{Saudi Arabian Oil Company}{Dhahran, KSA}
          \resumeItemListStart
            \resumeItem{Project manager leading a team of scouts to create an application and digitize historical paper records for the old expatriate graveyard located in the LIP Dhahran, Saudi Arabia.}
            \resumeItem{Developed a database to store all the historical records using SQL and Microsoft Access and incorporated a GIS frontend with the help of the Saudi Aramco surveying group.}
          \resumeItemListEnd
          \vspace{-5pt}
          
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------Leadership / Achievements---------------
\section{Leadership / Achievements}
    \vspace{-4pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading{Endorsement by former Minister of Energy}{Dhahran, KSA}
            \resumeItemListStart
                \resumeItem{Recognized by the former CEO of Saudi Aramco and Minister of Energy Khalid Al-Falih for my creation of the digital expatriate graveyard application.}
            \resumeItemListEnd
        \resumeSubheading{Boy Scouts of America}{June 2017}{Eagle Scout}{Dhahran, KSA}
            \resumeItemListStart
                \resumeItem{Lead other scouts teaching them the skills they needed to earn badges and progress through the organization.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
